\documentclass[12pt]{article}

\usepackage[backend=biber]{biblatex}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{esint}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{blindtext}
\usepackage{fancyhdr}

\addbibresource{/home/krttd/documents/UAH.bib}

\pagestyle{fancy}
\lhead{}
\chead{}
\cfoot{}
\rhead{Dodson \thepage}

\renewcommand*{\bibfont}{\normalsize}

\titleformat{\section}
{\large}{}{0em}{}[\titlerule]


\begin{document}

\begin{minipage}[h]{.1\textwidth}
    To:

    From:

    Date:

    Subject:
\end{minipage}
\begin{minipage}[h]{.8\textwidth}


    Dr. Ryan Weber

    Mitchell Dodson

    April 17, 2020

    Term Project Progress Report
\end{minipage}

\section{Introduction}

My Eh 301 term project will consist of a series of technical documents concerning custom software for a locally-hosted blog database, website, and publishing system. Now that I am 10 days away from turning in the project, my focus is soon to transition towards making the actual documents; I'm nearly finished designing and developing the software, making appropriate diagrams, and conducting interviews and tests.

\section{Completed Work}

The first thing I focused on was the development of the abstract design principle of each component of the blog. In doing so, I developed several of the UML diagrams that will be included in the largest section of the final term document. Additionally, I'm nearly finished with a working prototype version of the blog frontend, which should be ready for usability testing soon. Finally, I interviewed several of the actual researchers who will be publishing to the blog; these interviews helped me understand how to properly design the publishing API and command-line interface and will be used as references.

\section{Work Remaining}

Now that I'm nearly finished with the testing, diagramming, and interviewing, I need to start focusing on compiling everything. I've already made a template in \LaTeX for each document, which should work well with the UML diagrams and other images. I plan to conduct the user test with Ben and Shay on Sunday, Aril 19, and begin filling out these templates in the next few days. I may also reformat my bibliography.

\section{Challenges Faced}

This blog project was originally intended to be a sort of correlated effort between writing the actual software as a responsibility of my job and writing the documentation as a responsibility of this class. Unfortunately, my task assignment at my job unavoidably changed soon after I proposed the project, which meant I needed to develop almost all of the technical background for the blog off-the-clock in the time I would usually allocate to classes.  Furthermore, logistic complications (mostly the result of COVID-19) have seriously restricted the amount of time I have to work on this project and all other school-related responsibilities. These things have unfortunately left me a few days behind my project schedule.

\section{Timeline}

\begin{tabular}{l | l | l }
To Do&In Progress&Completed\\\hline
Format test data into report&High-level blog philosophy&Design publisher\\
Write and format publishing info&Module UML& interview researchers \\
write api descriptions&write publishing info sheet&finish frontend\\
&Frontend user test&\\


\end{tabular}

%\begin{tabular}{l | l l l }
%                  & time (sec) & references & comments \\\hline
%    comprehension & 102        & 4          & good explanation but nomenclature is hard to follow \\
%    iter          & 73         & 1          & file object initially confusing (\textit{guidance provided})\\
%    zip           & 130        & 2          & easy to understand \\
%    sort/lambda   & 362        & 7          & lambda is difficult to understand \\
%
%\end{tabular}

\nocite{Brooke18}
\nocite{Melbourne15}
\nocite{Ceta20}
\nocite{Andrew18}

\printbibliography
\end{document}
