\documentclass[11pt]{article}

\usepackage[backend=biber,style=mla]{biblatex}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{soul}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{esint}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{blindtext}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}

\addbibresource{/home/krttd/Documents/UAH.bib}

\doublespacing

\renewcommand*{\bibfont}{\normalsize}

\titleformat{\section}
{\large}{}{0em}{}[\titlerule]


\begin{document}

\begin{center}
        {\color{OliveGreen}\LARGE{Mitchell T. Dodson}}

        \vspace{1em}

\hrule

	\noindent
        \begin{minipage}[t]{.49\textwidth}
		\begin{singlespace}

		\noindent
		\hl{Jacobs Space Exploration}

		\noindent
		\hl{20320 Marshall Space Flight Center,}

		\noindent
		Huntsville, Al 35806

		\end{singlespace}
        \end{minipage}
        \begin{minipage}[t]{.49\textwidth}

		\vspace{1em}

                \hfill
                (270)-***-****

                \hfill
                mitchell.t.dodson@nasa.gov

        \end{minipage}
\end{center}


\vspace{2em}

\noindent
Dear Mr./Ms. ------,

\vspace{1em}
I was excited to find your job advertisement for \hl{Jacobs Space Exploration Group Summer Intern on the Jacobs} website today. I'm confident that I am an ideal candidate for this position, and I am happy to have the opportunity to apply to be a member of your team.

During my time as a Student Programmer for NASA SPoRT in the past year, I gained critical skills in \hl{communication and technical writing in LaTeX} while working closely with research scientists and internal SPoRT software engineers. My experience with collaboratively designing, creating, and documenting systems software, webpages, and data analysis programs have honed my ability to work together with colleagues and seniors and heed instructions effectively while working efficiently and intelligently on complicated problems with minimal need for supervision. Furthermore, my time-management and organization skills have been tested and proven under the pressure of working on both my Physics and Mathematics bachelors degrees while working 23+ hours per week at NASA. \hl{Lastly, the job advertisement for this position specifically mentions the need for ``strong customer relations skills.'' As a web developer at NASA SPoRT, I was responsible for communicating detailed requirements with customer departments and meeting rapid deliverables, which granted me an intuition for interacting efficiently and politely with customers, and for understanding and meeting their needs.}

I am looking forward to this position with \hl{Jacobs} allowing me to further my capabilities and gain experience that will allow me to excel as a professional. I am sure that I have a lot to offer \hl{Jacobs} as a Student Intern, and I greatly look forward to meeting and working with you in person.

\noindent
With sincere gratitude,

\vspace{1em}

\noindent
\textit{ signature }

\vspace{1em}

\noindent
\textbf{Mitchell T. Dodson}

\printbibliography
\end{document}
