\documentclass[11pt]{article}

\usepackage[backend=biber,style=mla]{biblatex}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{esint}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{blindtext}
\usepackage{fancyhdr}

\addbibresource{/home/krttd/Documents/UAH.bib}

\doublespacing

\pagestyle{fancy}
\lhead{}
\chead{}
\cfoot{}
\rhead{Dodson \thepage}

\renewcommand*{\bibfont}{\normalsize}

\titleformat{\section}
{\large}{}{0em}{}[\titlerule]


\begin{document}

Mitchell Dodson

Dr. Ryan Weber % Professor

Eh 301 % class

March 16, 2020 % date

\begin{center}\Large
Proposal Analysis
\end{center}

I chose the NASA SBIR proposal...

\begin{enumerate}

	\item{This proposal is ultimately very specific about the service it intends to provide. The writers to a great job of outlining the function and implementation of EHBs and other technologies in much detail (Sections 2, 3, and 4) as well as providing many specific potential use cases for EHB-based management (Section 10). however it is initially somewhat difficult to understand abstractly what purpose EHBs serve. Without background knowledge on what NASA SBIR does as an institution, it is difficult for readers discern the aim of the project on the whole. This would be remedied if the writers included more information on the system that EHBs and web-based ``Requirements Capture Tools'' are designed to replace.}

	\item{This proposal very strongly demonstrates knowledge of what the funders need. Much of section 4.3 is dedicated to outlining the ways that EHBs reduce costs and increase efficiency when generating documentation for a project. Furthermore, Coney Island Inc. provides a very long and descriptive list of NASA applications as well as commercial use cases for the technology (Section 10).}

	\item{Coney Island Inc. establishes credibility directly by providing a brief biography of every staff member including a description of what role they will play during the completion of the contract as well as an overview of each team member's experience pertaining directly to their project responsibilities. Additionally, Coney Island Inc. indirectly implies their credibility by providing schedules, a breakdown of personnel allocation, as well as lucid descriptions of each stage of the project's completion.}

\end{enumerate}

\printbibliography
\end{document}
