\documentclass[11pt]{article}

\usepackage[backend=biber,style=mla]{biblatex}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{esint}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{blindtext}
\usepackage{fancyhdr}
\usepackage{soul}
\usepackage[dvipsnames]{xcolor}

\addbibresource{/home/krttd/Documents/UAH.bib}

\doublespacing

\renewcommand*{\bibfont}{\normalsize}

\titleformat{\section}
{\large}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
        {\color{OliveGreen}\LARGE{Mitchell T. Dodson}}

        \vspace{1em}

\hrule

        \noindent
        \begin{minipage}[t]{.49\textwidth}
                \begin{singlespace}

                \noindent
		\hl{Radiance Technologies}

                \noindent
		\hl{310 Bob Heath Drive}

                \noindent
		Huntsville, AL 35806

                \end{singlespace}
        \end{minipage}
        \begin{minipage}[t]{.49\textwidth}

                \vspace{1em}

                \hfill
                (270)-***-****

                \hfill
                mitchell.t.dodson@nasa.gov

        \end{minipage}
\end{center}

\vspace{2em}

\noindent
Dear Mr./Ms. ------,

\vspace{1em}
I was excited to find your job advertisement for \hl{Machine Learning Intern on the Radiance} website today. I am confident that I am an ideal candidate for this position, so I am happy to have the opportunity to apply to be a member of your team.

\hl{In addition to 2 years of academic experience using Python and C++, my time as a Student Programmer for NASA SPoRT in the past year allowed me to gain critical skills with Python while working on GOES satellite data processing and image manipulation, including some experience creating keras-based machine learning agents}, all while working closely with research scientists and internal SPoRT software engineers.

\hl{In addition ot my technical skills, my ability to communicate with colleagues and seniors has been honed by collaboratively designing, creating, and documenting systems software, webpages, and data analysis programs. Due to the high levels of accountability and rapid project turnover time at NASA, I have an aptitude for} heeding instructions effectively while working efficiently and intelligently on complicated problems while requiring minimal need for supervision. Furthermore, my time-management and organization skills have been tested and proven under the pressure of working on both my Physics and Mathematics bachelors degrees while working 23+ hours per week at NASA.

I am looking forward to this position with \hl{Radiance} potentially allowing me to further my capabilities and gain experience that will allow me to excel as a professional. I am sure that I have a lot to offer \hl{Radiance} as a \hl{Machine Learning Intern}, and I greatly look forward to meeting and working with you in person.

\noindent
With sincere gratitude,

\vspace{1em}

\noindent
\textit{ signature }

\vspace{1em}

\noindent
\textbf{Mitchell T. Dodson}

\printbibliography
\end{document}
