\documentclass[12pt]{article}

\usepackage[backend=biber,style=mla]{biblatex}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{esint}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{blindtext}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}

\addbibresource{/home/krttd/Documents/UAH.bib}

\renewcommand*{\bibfont}{\normalsize}

\titleformat{\section}
{\large}{}{0em}{}[\titlerule]


\begin{document}

\begin{center}
        {\color{OliveGreen}\LARGE{Mitchell T. Dodson}}

        \vspace{1em}

	\noindent
        \begin{minipage}[t]{.48\textwidth}

		\noindent
                Huntsville, AL 35805

		\noindent
                ****-* John Wright Drive

        \end{minipage}
        \begin{minipage}[t]{.48\textwidth}

                \hfill
                (270)-***-****

                \hfill
                mitchell.t.dodson@nasa.gov

        \end{minipage}
\end{center}

\hrule

\vspace{2em}

\noindent
Dear Mr./Ms. ------,

\vspace{1em}
I was excited to find your job advertisement for Jacobs Space Exploration Group Summer Intern on the Jacobs website today. I'm confident that I am an ideal candidate for this position, and I am happy to have the opportunity to apply to be a member of your team.

During my time as a Student Programmer for NASA SPoRT in the past year, I gained critical skills in communication and technical writing in LaTeX while working closely with research scientists and internal SPoRT software engineers. My experience with collaboratively designing, creating, and documenting systems software, webpages, and data analysis programs has honed my ability to communicate with my seniors and heed instructions effectively while working efficiently and intelligently on complicated problems with minimal need for supervision

Furthermore, in addition to being a lifelong aptitude of mine, my time-management and organization skills have been tested and proven under the pressure of studying for both my Physics and Mathematics bachelors degrees while working 23+ hours per week at NASA.

In addition to my academic continence, I believe one of my personally defining characteristics emerges from my daily struggle with irritable bowel syndrome (IBS). This internship's job description specifically mentions that candidates should be able to multi-task and transition quickly between assignments; the constant state of my condition has trained me to adopt careful planning and perpetual readiness as second nature, which will doubtless make me indespensible in the fast-paced environment of Jacobs.

I am looking forward to this position with Jacobs allowing me to further my capabilities and gain experience that will allow me to excel as a professional. I am sure that I have a lot to offer Jacobs as a Student Intern, and I greatly look forward to meeting and working with you in person.

\vspace{1em}

\noindent
With sincere gratitude,

\vspace{1.5em}

\noindent
\textit{ signature }

\vspace{1.5em}

\noindent
\textbf{Mitchell T. Dodson}

\printbibliography
\end{document}
